\documentclass[12pt]{article}
\renewcommand{\baselinestretch}{1.5}
\usepackage{threeparttable}
\usepackage{pdflscape}
\usepackage{amsmath}
\usepackage{amstext}
\usepackage{color}
\usepackage{pgffor}
\usepackage{graphicx}
\parindent=.2in
\evensidemargin=.05in 
\oddsidemargin=-.05in  
\topmargin=-0.05in
\textwidth=6.4in 
\textheight=8in
\newcommand{\sym}[1]{\rlap{$#1$}}
\newtheorem{fact}{Stylized Fact} 
\newtheorem{theorem}{Theorem}
\newtheorem{corollary}{Corollary}
\newtheorem{definition}{Definition}
\newtheorem{lemma}{Lemma}
\newtheorem{prop}{Proposition}
\newtheorem{assumption}{Assumption}
\newtheorem{remark}[theorem]{Remark}
\newtheorem{solution}[theorem]{Solution}

\begin{document}

\title{Extra-curricular Activities Classification} 
  
 \author{Yu Wang\\
 Ryerson University}

\date{\today}
\maketitle

The purpose of the task is to classify user-supplied descriptions of extra-curricular activities quantitatively. 

\begin{enumerate}
\item I provide some examples below:
\item File {\itshape sample\_read\_extra\_curricular.txt} contains user-supplied descriptions. File {\itshape sample\_classify\_extra\_curricular.csv} contains the classification spreadsheet. 
\item Classify the extra-curricular descriptions based on following dimensions:
\begin{itemize}
\item {\itshape\textcolor{blue}{Greek}}: Any Greek life (membership in fraternal societies with names consisting of only greek letters.) For instance, ``Phi Alpha Delta'' counts as a Greek society. Sometimes the user just vaguely specifies that he has ``fraternal experiences''; count that as Greek too. However, if the user does not explicitly state that the organization contains Greek letters or is a fraternal society, there is no need to Google whether it is a Greek society or not; just treat it as non-Greek student society. 
\item {\itshape \textcolor{blue}{Community/Volunteer}}: Any volunteering services or community work.
\item {\itshape \textcolor{blue}{Athletic/Varsity}}: Any sports achievements or sports club membership.
\item {\itshape \textcolor{blue}{Non-Greek Student Societies}}: Any activities in student government, organizations, societies, student-run journals, or any other university campus activities. Some users say that they have ``EC'' experiences, treat those as Non-Greek Student Society experience. 
\item {\itshape \textcolor{blue}{Military}}: Any military service. 
\item {\itshape \textcolor{blue}{Overseas}}: Any overseas experience (including study, work, internship, exchange, etc)
\item {\itshape \textcolor{blue}{Legal Internship}}: Any internship or summer work experience related to legal work, paralegal work, courts, or politics. Sometimes the user does not specify whether it is work experience or internship experience; in such cases, treat it as work experience. 
\item {\itshape \textcolor{blue}{Non-Legal Internship}}: Any non-legal internship/summer work.
\item {\itshape \textcolor{blue}{Legal Work Experience}}: Any full-time and part-time work experience related to legal work, paralegal work, courts, or politics. Again, sometimes the user does not specify whether it is work experience or internship experience; in such cases, treat it as work experience. 
\item {\itshape \textcolor{blue}{Non-Legal Work Experience}}: Any full-time and part-time non-legal-related work experience, including campus work such as tutoring, research assistantship, and teaching assistantship. 
\item {\itshape \textcolor{blue}{Strong Letters}}: Any good letters. A commonplace acronym for ``letter of recommendations'' is LOR.
\item {\itshape \textcolor{blue}{Leadership}}: Any leadership responsibilities in any categories above. This includes implied leadership. For instance, some users describe themselves as presidents of clubs, ``holding top positions'', or ``starting or founding'' an organization; count all those as leadership, even if the word ``leadership'' does not explicitly appear. 
\end{itemize}
\item If the user has mentioned certain experience, fill {\itshape 1} to the spreadsheet. Otherwise, leave it blank.
\item If the user reports work experience/internship but does not specify what it is, treat it as non-legal ones. 
\item The word ``softs'' refer to ``Non-test-score characteristics''. Some users may describe themselves as having ``average softs'', which means that they have comparable activities as their peers. However, if they do not explicitly describe what these experiences are, ignore the word ``softs''.  
\end{enumerate}

\end{document}